Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-04 article.tex
correctly explain directivity

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
% TODO better link
%      add that we make the count matrix antisymmetric (count - count.T)
%      say that we normalize and stack
%      specify f_1 and f_2
In the hope to improve performance, some causal information (directivity of
the links) were added by stacking the partial correlation score matrix
with

from the
data by comparing activity of each couple of neurons between two subsequent
time steps. The directivity method tries to detect variation of fluorescence
signal of a neuron $j$ due to a neuron $i$. A connectivity score
between the two neurons $i$ and $j$ is given by
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2])
\]

where $f_1$ and $f_2$ are parameters of the method and $I(\bullet)$ is the
indicator function. Finally, a

>>>>

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
In our last submission in hope to improve performance, some causal information
(directivity of the links) were added by stacking the partial correlation score
matrix with an pairwise activation heuristics. This method computes an
activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
$j$ due to a neuron $i$ over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function.
